---
title: "Artificial Neural Network"
author: "Jiyi Jiang"
date: "06/01/2015"
output: html_document
---

This is the function of modeling neural network.

```{r}

x=1
y=1
f=outer(x,y,function(x,y)(matrix(c(0.5,1,1.5),1,3)%*%tanh(matrix(c(-3,-1,3,-2,3,-1),3,2)%*%matrix(c(x,y),2,1)+matrix(c(6,-6,-3),3,1)))+3) 

x=sample.int(5,n=100)/100

```

We build up the function which models the behavior of graph on slides 56 by taking the vector multiple by weight and add by bias. 
Then assign a number to each color, and repeat the previous process.
You can also embed plots, for example:

```{r}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

---
title: "Artificial Neural Network Continue"
author: "Jiyi Jiang"
date: "06/02/2015"
output: html_document
---
create a for loop
```{r}
v=c(1:100)
w=c()
for(i in 1:100){w[i]=v[i]+10}
f
```

```{r}
v=c(1:1000000)
f=function(x){x+10}
sapply(v,f)

 lapply(x,function(x){matrix(c(x,x+1),2,1)})
```


class(lapply(v,f)) "list"
class(lapply(l,f)) "list"
class(sapply(v,f)) "numeric"
class(lapply(l,f)) "matrix"

mapply
used when multiple variables are in one function.
```{r}
 l=list(x=1:10,y=1:10)
 f=function(x,y){x+y}
 mapply(f,l$x,l$y)
```
02

l
```{r}
 l=lis(1,2)
```
